---
title: "Exercise 1"
author: "Ashish Das"
date: "04/08/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Name = Ashish Das
## RegNo = 19BCE1160

## 1. Convert TRUE to an integer
```{r}
as.integer(TRUE)
```

## 2. Make this quote into an R string– “Do you think this is a game?”, he said. “No, I think Jenga’s a game”, Archer responded.
```{r}
str1 <- "Do you think this is a game?"
str2 <- ", he said."
str3 <- "No, I think Jenga's a game, Archer responded"
str1
str2
str3
```
## 3. Assign an integer value to two variables p & q.
```{r}
p<-8L
q<-2L
p
q
```

## 4. Use R as a calculator to do basic arithmetic operations on p &q and store each result in different variables.
```{r}
a<-p+q
a
b<-p-q
b
c<-p*q
c
d<-p/q
d
```

## 5. Calculate sqrt(p) and perform log2 transformation on the result.
```{r}
r<-sqrt(p)
r
log2(r)
```

## 6. Calculate the 10-based logarithm of 100 and multiply the result with cosine of π.
```{r}
s<-log10(100)
s
s*cos(pi)
```

## 7. Create a vector ‘x’ using : operator from -2 to 2.
```{r}
x<--2:2
x
```

## 8. Create a vector ‘y’ using c() with values 1 to 10. What is the dimension of y and length of y.
```{r}
y<-c(1,2,3,4,5,6,7,8,9,10)
y
length(y)
dim(y)
```

## 9. Create two vectors small and caps with first 5 alphabets in lower case and last 5 alphabets in upper case respectively. Bind it row and columnwise.
```{r}
small<-c("a","b","c","d","e")
small
caps<-c("V","W","X","Y","Z")
caps

rbind(small,caps)
cbind(small,caps)
```

## 10. Create a matrix M=[1,4,3;−2,8,6;5,−1,7] and find MxMxM.
```{r}
M<-matrix(c(1,4,3,−2,8,6,5,−1,7),nrow = 3,ncol = 3,byrow = TRUE)
M
M*M*M
```

## 11. Find the result of elementwise multiplication of M by M.
```{r}
M*M
```

## 12. Find the transpose, inverse and determinant of M.
## a) Transpose:
```{r}
t(M)
```
## b) Inverse:
```{r}
solve(M)
```
## c) Determinant:
```{r}
det(M)
```



