title: "Exercise3"
author: "Ashish Das"
date: "8/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Ashish Das
# 19BCE1160

## Ex-3 Data Manipulation using dplyr package

## Display the structure of the data survey.
```{r}
library(MASS)
data("UScereal")
str(UScereal)
UScereal
```
## Obtain a data frame called “newUScereal” by removing all ‘na’ values in “UScereal” data of MASS package 
```{r}
newUScereal <- na.omit(UScereal)
newUScereal
```
```{r}
library(dplyr)
cat("Installed and Imported dplyr package")
```

## 1.	Filter 5 cereals.with calorie higher than 100.
```{r}
newUScereal %>%
  filter(calories > 100) %>%
  head(5)
```
## 2. Filter 8 cereals.with protein higher than 5.
```{r}
newUScereal %>%
  filter(protein > 5)%>%
  head(8)
```
## 3.	Display all cereals whose manucafutrer is "G".
```{r}
newUScereal %>%
  filter(mfr=='G')
```
## 4.	Display random 5 rows of fat and sodium cereals. 
```{r}
newUScereal %>%
  dplyr::select(fat, sodium)%>%
  sample_n(5)
```
## 5.	Display random 5% of the rows of sugars and carbo both greater or equal to 12.
```{r}
newUScereal %>%
  filter(sugars >= 12 & carbo >= 12)%>%
  dplyr::select(sugars, carbo)%>%
  sample_frac(.5)
```

## 6.	Arrange all cereal in sugars conents that are greater than 10.00 in descending order.
```{r}
newUScereal %>%
  filter(sugars > 10 )%>%
  arrange(desc(sugars))
```
## 7.	Arrange all cereal in protein conents that are less than than 10.00 in descending order.
```{r}
newUScereal %>%
  filter(protein < 10 )%>%
  arrange(desc(sugars))
```

## 8.	Introduce a new column difference which contains the value as difference between the calorie and and display it along with manufacturer.
```{r}
newUScereal %>%
  mutate(difference=calories-protein)%>%
  dplyr::select(mfr, difference)
```

## 9.	Display the average of calories manufactured by G. 
```{r}
newUScereal %>%
  filter(mfr == 'G') %>%
  group_by(calories) %>%
  summarise(average=mean(calories))
```
## 10.	Find the maximum shelf of calories manufactures by N.
```{r}
newUScereal %>%
  filter(mfr == 'N') %>%
  group_by(shelf) %>%
  summarise(maximum = max(shelf))
```