title: "Exercise3"
author: "Ashish Das"
date: "8/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Ashish Das
# 19BCE1160

## Ex-3 Data Manipulation using dplyr package

## Display the structure of the data survey.
```{r}
library(MASS)
data("survey")
str(survey)
```
## Obtain a data frame called “newsurvey” by removing all ‘na’ values in “survey” data of MASS package 
```{r}
newsurvey <- na.omit(survey)
newsurvey
```

## 1.	Install the dplyr package and import it.
```{r}
library(dplyr)
cat("Installed and Imported dplyr package")
```

## 2.	Filter the top 5 male left handers.
```{r}
newsurvey %>%
  filter(Sex=="Male", W.Hnd=="Left") %>%
  head(5)
```
## 3.	Display all female right handers who keep right on top while clapping.
```{r}
newsurvey %>%
  filter(W.Hnd=='Right'& Sex=='Female'& Clap=='Right')
```
## 4.	Display all students who never exercise.
```{r}
newsurvey %>%
  filter(Exer=='None')
```
## 5.	Display random 5 rows of gender, age and writing hand columns of the students.
```{r}
newsurvey %>%
  dplyr::select(Sex, Age, W.Hnd)%>%
  sample_n(5)
```
## 6.	Display random 5% of the rows of age, pulse rate and writing hand span of female left handers.
```{r}
newsurvey %>%
  filter(Sex == 'Female'& W.Hnd =='Left')%>%
  dplyr::select(Sex,Age, Pulse, Wr.Hnd)%>%
  sample_frac(.5)
```

## 7.	Arrange all male left handers according to descending order of their heights.
```{r}
newsurvey %>%
  filter(W.Hnd=='Left'& Sex=='Male')%>%
  arrange(desc(Height))
```

## 8.	Introduce a new column hand_span which contains the value as difference between the span of writing hand and non-writing hand and display it along with gender, writing hand and non-writing hand span.
```{r}
newsurvey %>%
  mutate(hand_span=Wr.Hnd-NW.Hnd)%>%
  dplyr::select(Sex, Wr.Hnd, NW.Hnd, hand_span)
```

## 9.	Display the average writing span of male and female left handers.
```{r}
newsurvey %>%
  filter(W.Hnd == 'Left') %>%
  group_by(Sex) %>%
  summarise(average=mean(Wr.Hnd))
```
## 10.	Find the maximum pulse rate of male left and right handers.
```{r}
newsurvey %>%
  filter(Sex == 'Male') %>%
  group_by(W.Hnd) %>%
  summarise(average=max(Pulse))
```