---
title: "ex-4 = Data Cleaning"
author: "Ashish Das"
date: "24/08/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# NAME - ASHISH DAS
# REG NO - 19BCE1160


```{r}
nyc <- read.csv("nyc.csv")
dim(nyc)
str(nyc)
View(nyc)


nyc_clean <- na.omit(nyc)
sum(is.na(nyc_clean))

sum(is.na(nyc$id))
sum(is.na(nyc$name))
sum(is.na(nyc$host_id))
sum(is.na(nyc$host_name))
sum(is.na(nyc$neighbourhood_group))
sum(is.na(nyc$neighbourhood))
sum(is.na(nyc$latitude))
sum(is.na(nyc$longitude))
sum(is.na(nyc$room_type))
sum(is.na(nyc$price))
sum(is.na(nyc$minimum_nights))
sum(is.na(nyc$number_of_reviews))
sum(is.na(nyc$last_review))
sum(is.na(nyc$reviews_per_month))
sum(is.na(nyc$calculated_host_listings_count))
sum(is.na(nyc$availability_365))


unique(nyc$reviews_per_month)

mean(nyc$reviews_per_month,na.rm = TRUE)

library(dplyr)
library(tidyverse)

nyc %>%
  summarize(avg=mean(reviews_per_month,na.rm=TRUE),med=median(reviews_per_month,na.rm=TRUE))

nyc <- nyc %>%
  mutate(reviews_per_month=replace(reviews_per_month,is.na(reviews_per_month),median(reviews_per_month,na.rm=TRUE)))

sum(is.na(nyc$reviews_per_month))
names(nyc)
view(nyc)

str(nyc)
```
# Summary
## checked for total na values in original dataset "nyc.csv"
## checked all the columns indivisually for na Values.
## checked if the data type was appropriate for the particular column or not
## found na values in reviews_per_months 
###  - cleaned the data for na values
###  - found mean and median for the data
###  -replaced na values with median because in a large dataset there is a huge difference between higest and lowest values so median would be more  appropriate option.
## displayed the final table
