title: "Exercise5"
author: "Ashish Das"
date: "9/7/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Ashish Das
# 19BCE1160

```{r}
library(dplyr)
library(help="graphics")
library(lattice)
```

### Use the newsurvey data obtained by cleaning ‘na’ values in survey data of MASS package to do the following:
```{r}
library(MASS)
data("survey")
str(survey)
```

```{r}
library(dplyr)
```

### Cleaning up the dataset
```{r}
newsurvey <- na.omit(survey)
```


### Checking if the `newsurvey` has any NA values left
```{r}
sum(is.na(newsurvey))
```


### 1.	Plot a bar graph for the number of male and female participants in the survey. Provide the title as “Male and Female participants”, y-axis label as “frequency” and specify the colours for the bars.
```{r}
barplot(table(newsurvey$Sex),col=c("red","green"), main = "Male and Female participants", ylab = "Frequency")
```


### 2. Plot a bar graph for the number of left handers and right handers in the survey. Provide the title as “Left Handers and Right Handers”, y-axis label as “count” and specify the colours for the bars.
```{r}
barplot(table(newsurvey$W.Hnd),col=c("red","green"), main = "Left Handers and Right Handers", ylab = "Count")
```


### 3. Plot the distribution between male left handers and female left handers using bar chart. Provide the title as “Female Left Handers and Male Left Handers" , y-axis label as “count” and specify the colours for the bars.
```{r}
left_hnd <- newsurvey %>%
    filter(W.Hnd=="Left")
barplot(table(left_hnd$Sex),col=c("red","green"), main = "Female Left Handers and Male Left Handers", ylab = "Frequency")
```


### 4.	Draw the distribution of smoking habits of male left handers using pie chart.
```{r}
male_lefty <- newsurvey%>%
  filter(Sex=="Male", W.Hnd=="Left")
unique(male_lefty$Smoke)
table(male_lefty$Smoke)

pie(table(male_lefty$Smoke),radius=1)
```

### 5.	Draw the histogram of age distribution with the title as ‘Age distribution’ and xlabel as ‘Age range’ and ylabel as ‘frequency’.
```{r}
hist(newsurvey$Age, main="Age distribution", ylab = "Frequency", xlab = "Age range")
```

### 6.	Reveal the relationship between the age and writing hand span using scatter plot.
```{r}
plot(newsurvey$Age, newsurvey$Wr.Hnd)
```

### 7.	Draw the boxplot for pulse rate to analyse the five summary statistics. Provide appropriate title and label.
```{r}
summary(newsurvey$Pulse)
boxplot(newsurvey$Pulse, main="Boxplot for the Pulse rate", ylab="Count", xlab="Pulse Rate")
```

### 8.Frame any 3 questions on data visualization to graphically depict the data that you have chosen for cleaning.
```{r}
nyc <- read.csv("nyc.csv")
str(nyc)
nyc_clean <- na.omit(nyc)
```
### 8.a. Draw a density plot for latitute for the data set
```{r}
densityplot(nyc_clean$latitude)
```

### 8.b. Draw a splom for the data set.
```{r}
splom(nyc_clean[c(1,3,4)])
```
### 8.c. Plot a bar graph for the price in the survey. Provide the title as “Price over the years”, y-axis label as “Amount in rupees”.
```{r}
barplot((nyc_clean$price),col=c("green"), main = "Price over the years", ylab = "Amount in rupees")
```