---
title: "Ex-7 19BCE1160"
author: "Ashish Das"
date: "28/09/2021"
output: html_document
---

## ASHISH DAS
## REGNO - 19BCE1160

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Create a data frame ‘newsurvey’ that contains the survey data in MASS package after removing the NA values. Use it for answering following queries:
```{r}
library(MASS)
library(dplyr)
library(ggplot2)
data("survey")
newsurvey <- survey
nrow(newsurvey)
newsurvey <- newsurvey[complete.cases(newsurvey),]
nrow(newsurvey)
str(newsurvey)
```

#### 1. How many male and female students participated in the survey?.
```{r}
gender_freq=table(newsurvey$Sex)
gender_freq
```

#### 2. Find the relative frequency distribution of male and female participants and display them with the precision of two decimal places.
```{r}
old=options(digits=2)
size=nrow(newsurvey)
gender_relfreq=gender_freq/size
gender_relfreq
```

#### 3. Display the male right hander and female right hander in the column format.
```{r}
hander_freq=table(newsurvey$W.Hnd)
cbind(hander_freq)
```

#### 4. What percentage of male left handers never smokes?
```{r}
total = newsurvey %>%
  filter(Sex=='Male' , W.Hnd=='Left')%>%
  summarize(cnt = n())
smokers = newsurvey %>%
  filter(Sex=='Male', W.Hnd == 'Left', Smoke!='Never') %>%
  summarise(cnt=n())
(smokers/total)*100
```

#### 5. Find the range of students’ age participated in the survey.
```{r}
duration=newsurvey$Age
range(duration)
```

#### 6. Break the age range into non-overlapping sub-intervals by defining a sequence of equal distance break points of 10 by rounding the range to nearest integer.
```{r}
breaks=seq(10,70,by=10)
breaks
```

#### 7. Find the distribution of the age range according to the sub-intervals with cut with its right boundary opened. Display it in column form.
```{r}
duration_cut=cut(duration,breaks,right=FALSE)
duration_freq=table(duration_cut)
cbind(duration_freq)
```

#### 8. Which age range of students has mostly participated in the survey.
```{r}
which.max(duration_freq)
```

#### 9. Compute the mean, variance and standard deviation of the age of the students participated in the survey.
```{r}
cat("Mean: ", mean(newsurvey$Age))
cat("Variance: ", var(newsurvey$Age))
cat("Standard Deviation: ", sd(newsurvey$Age))
```

#### 10.Which category of exercise students has the maximum writing hand span 
```{r}
exer_cat = newsurvey%>%
            arrange(desc(Wr.Hnd))%>%
              select(Exer)
head(exer_cat,1)
```

#### 11. Compute the covariance and correlation between age and writing span
```{r}
waiting=newsurvey$Wr.Hnd
cov(duration,waiting)

cor(duration,waiting)
```

#### 12. Display the 20%,50% and 70% percentile of the age data.
```{r}
percentile_age=quantile(duration, c(.20,.50,.70))
percentile_age
```

```{r}
library(MASS)
head(painters)
str(painters)
```
#### 13. What percentage of painters use color more than 15 and expression less than 5?
```{r}
hsef=painters%>%
  filter(Colour>=15, Expression<5)
hsefperc <- nrow(hsef)/nrow(painters)*100  
hsefperc
```

#### 14. What percentage of painters use composition = 10 and drawing less than 5?
```{r}
hsef=painters%>%
  filter(Composition==10, Drawing<5)
hsefperc <- nrow(hsef)/nrow(painters)*100  
hsefperc
```
#### 15. Find range of values in Eruptions
```{r}
duration=faithful$eruptions
range(duration)
```

